Time Series Modeling of Subdiffusive Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-10-06 Ben_Manuscripts/stochastic_transport/Draft.tex
MRS comments.

\title{Time Series Modeling of Subdiffusive Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
%MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \begin{abstract}

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories, in order
  to predict solute mean squared displacements (MSDs). With our first model, based
  on the anomalous diffusion literature, we show how solute dynamics can be modeled as
  a fractional diffusion process subordinate to a continuous time random walk.
  We parameterize the distribution of dwell times, hop lengths between dwells and
  correlation between hops. We explore 2 variations of the model. The first variation
  applies a single set of parameters to the solutes and the second applies 2 sets
  of parameters based on the solute's radial distance from the closest pore center.
  Our second model, an adaptation of Markov state models, treats the system
  as a Markov process where we quantify the transitions between a set of 
  explicitly defined states. We incorporate the magnitude and temporal correlation
  of positional fluctuations into each state and transitions between states to gain
  further insight and allow us to predict solute MSDs. We show that our models 
  reasonably reproduce MSDs calculated from molecular simulations. The anomalous 
  diffusion shows superior predictive performance, in many cases exactly reproducing
  MD results within error. We use the parameters of each model to offer additional mechanistic
  insight. These parameters are important for identifying specific differences in 
  solute transport behavior. The differences suggest modifications that can be
  made to LLC membrane monomers in order to increase or reduce selectivity towards a 
  specific solute.

  \end{abstract}

@@

  Mathematical descriptions of transport in complex separations membranes are a powerful 
  way to understand mechanisms and formulate membrane design principles. The complexity
  of a model generally parallels the complexity of the transport mechanism at hand, as
  well as the desired outputs. In dense homogeneous membranes, the solution-diffusion 
  model can extract diffusion and partition coefficients and has successfully predicted
  solute transport rates. Analogously, pore-flow models yield predictions of diffusion 
  coefficients and solute transport rates in nanoporous membranes.~\cite{wijmans_solution-diffusion_1995}
  Modern single particle tracking approaches take us beyond continuum modeling and 
  allow us to characterize complex diffusive behavior.~\cite{manzo_review_2015} 
  At the molecular level, one can use molecular dynamics (MD) simulations to study both
  single particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
  All of these approaches facilitate speculation on the molecular origins of separations
  by attempting to give a more intuitive understanding of how solutes move as a function
  of their environment, in turn suggesting experiments that should be run.

  % BJC1: tie this paragraph into above by commenting that highly selective membranes
  % often have complex mechanistic reasons that aren't explained by simpler models
  % BJC3:maybe change this paragraph to just be examples of highly selective separations, not
  Facile design of highly selective separations membranes is desirable in numerous
  applications. The ability to efficiently separate ions from saline water sources using 
  membranes has been actively pursued for years in an effort to create potable water for 
  people in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  there is a strong interest in creating breathable barriers to chemical warfare agents
  which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
  The speed at which we achieve these or any other selective separation will be 
  heavily influenced by the quality of insights gained by the modeling approaches above.

@@

%  Regardless of which LLC phase ones studies, one must contend with the large chemical design
%  space available to design these types of membranes. 
  We want to use a molecular model in order to understand how we can leverage the large 
  chemical space available for LLC monomer design in order to create efficient solute-specific
  separations. To date, only a limited subset of LLC monomers have been studied in membrane
  applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, there have been shown selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling provides the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms allowing us to move beyond 
  traditional Edisonian design.

@@

  Researchers have developed a rigorous theoretical foundation for describing the 
  motion of particles exhibiting non-Brownian, or anomalous, transport behavior.
  The tools introduced by fractional calculus are instrumental to this theory. They
  allow us to generalize the normally linear diffusion equation to fractional
  derivative orders, providing descriptions of a much more diverse set of behavior.~\cite{klages_anomalous_2008}

@@

  % BJC2: moved this from below
  Our first modeling approach is based on the anomalous diffusion literature, 
  applying the mathematical formalism describing subdiffusive transport to observed
  solute trajectories. We fit anomalous diffusion models in two ways: First, based 
  on a single set of parameters. Second, we use a two-state approach incorporating
  two sets of parameters based on a solute's radial distance from the closest pore center.

  While elegant, pure anomalous diffusion theory may in some cases give only a 
  qualitative understanding of transport mechanisms. Complex temporal relationships in 
  between hops may have a significant effect on the average MSD. Inhomogeneity of 
  a medium or multiple types of interactions may lead to a number of distinct 
  diffusive regimes. In this case, a state based model may be useful.

@@

  Our second modeling approach applies an extended MSM framework to a relatively 
  small set of known states based on the three observed solute trapping mechanisms.
  Standard MSMs assume first order kinetics and are typically applied 
  towards determining equilibrium populations of and the transitions between 
  various state configurations.~\cite{bowman_using_2009} We extend the framework
  to include dynamics within states and between jumps. That is we parameterize 
  and incorporate into our model the magnitude and temporal correlation of
  fluctuations in solute position while in each state as well as during transitions
  to different states. 
  %Temporal correlation in position has a significant influence on 
  %a solute's mean squared displacement.

@@

  We studied transport of solutes in the H\textsubscript{II} phase using an atomistic
  molecular model of four pores in a monoclinic unit cell with 10 \% water by weight 
  (see Figure~\ref{fig:membrane_structure}). Approximately one third of the water 
  molecules occupy the tail region with the rest near the pore center. We chose to
  focus our study on the 10 wt \% water system because solutes move significantly 
  faster than in the 5 wt \% system studied previously. Appropriate stochastic 
  modeling requires that solutes sample the accessible mechanisms with representative
  probability.

@@

  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
  to collect ample data. We simulated the system with a time step of 2 fs at a pressure
  of 1 bar and 300 K controlled by the Parinello-Rahman barostat and the v-rescale 
  thermostat respectively. We recorded frames every 0.5 ns.

  We considered each system to be equilibrated when the solute partition between the 
  pore and tail region stopped changing. We excluded data collected before equilibration
  from our analysis. We plotted the solute partition versus time in Figure~\ref{S-fig:equilibration}
  of the Supporting Information in order to justify our choice of equilibration times
  for each solute.

@@

  % BJC3: x --> z since I'm measuring diffusion in the z direction?
  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, rather it follows a power law of the form:
  \begin{equation} 
  \langle x^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. A value of $\alpha_d < 1$ indicates a subdiffusive process, 
  while values of $\alpha_d = 1$ and $\alpha_d > 0$ are characteristic of Brownian and
  superdiffusive motion respectively.

@@

  %BJC3: removed ensemble MSD because it's not used
  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. If the underlying 
  subdiffusive process is not ergodic, like a pure CTRW, the time averaged MSD becomes
  linear.~\cite{meroz_toolbox_2015}

@@

  We believe that solute motion in the system studied here may be consistent with 
  subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
  the leading process is a CTRW. We observe hopping and trapping which is consistent
  with a CTRW along with negatively correlated hops which is consistent with FBM.

  One can characterize a CTRW process using the parameters which describe its dwell 
  time and hop length distributions. We used the \texttt{ruptures} python package in 
  order to automatically identify mean shifts in solute trajectories, indicating hops.\cite{truong_ruptures:_2018} 
  We used the corresponding hop lengths and dwell times between hops to construct 
  empirical distributions.

@@

  Assuming hops are correlated, solute behavior may be described by subordinated 
  fractional L\'evy motion (sFLM). The Hurst parameter can again be used to describe
  hop correlations because they share the same autocorrelation structure.~\cite{tikanmaki_fractional_2010}
  The autocovariance function for FLM is:
  \begin{equation}
    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)sin(\pi H)}
    \label{eqn:flm_autocovariance}
  \end{equation}
  where $E\big[L(1)^2\big]$ is the expected value of squared draws from the 
  underlying L\'evy distribution, effectively the distribution's 
  variance.~\cite{bishwal_maximum_2011} In general, most L\'evy stable distributions
  have an undefined variance due to their heavy tails. However, normalizing
  Equation~\ref{eqn:flm_autocovariance} by the variance of a finite number of draws
  from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
  See Section~\ref{S-section:H_estimate} of the Supporting Information for numerical
  simulations illustrating this point.  % BJC3: could use another reference proving mathematically what I show numerically

@@

  \subsubsection*{Multiple Dynamical Modes}

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This inspired two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
%  $\alpha$, $\sigma$, $H$ and, when the truncated power law is used, $\lambda$ parameters
%  fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  \subsubsection*{Simulating Anomalous Diffusion}

  We simulated models with all combinations of dwell and hop length distributions
  described above, summarized in Table~\ref{table:anomalous_models}. All models 
  include correlation between hops.
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{|c|c|c|}
	  \hline
	  Dwell Distribution                & Hop Length Distribution & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
	  \end{tabular}
	  \caption{We tested models with various modifications to the dwell and hop
	  length distributions. We incorporate correlation structure into all models.}\label{table:anomalous_models}
 \end{table}

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 10000 anomalous diffusion trajectories of length $T_{sim}$ in
  order to directly compare our model's predictions to MD simulations. $T_{sim}$ varied due to
  differing solute equilibration times. We constructed trajectories by simulating 
  sequences of dwell times and correlated hop lengths generated based on
  parameters randomly chosen from our bootstrapped parameter distributions. We 
  propagated each trajectory until the total time equaled or exceeded $T_{sim}~ \mu$s, then
  truncated the last data point so that the total time exactly equaled $T_{sim}~ \mu$s since
  valid comparisons are only possible between fixed length sFBM simulations. The
  power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
  decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
  We reported the time-averaged MSD after time lags 40 \% the length of the trajectory
  with corresponding 95 \% intervals.
  %BJC3: Not sure if 40 % above is too long. I could do 20

  When simulating 2 mode models, we determined the state sequence based on random 
  draws weighted by the appropriate row of the probability transition matrix. We 
  incorporated uncertainty into transition probabilities by drawing samples from a 
  two dimensional Dirichlet distribution (also called a beta distribution) with concentration parameters defined by 
  the count matrix.~\cite{bacallado_bayesian_2009} We drew hops and dwells based on
  the current state of the system. We used a single Hurst parameter to describe
  correlation between hops, independent of the solute's mode. Ideally, each mode
  would have its own Hurst parameter, but we did not observe enough long sequences
  of uninterrupted time spent in each mode with which to generate robust
  autocorrelation functions.

  %We also projected MSDs out to 1 second for each solute. % BJC3:??
  %BJC3: not sure how to cite fbm
  We used the python package \texttt{fbm} to generate exact simulations of FBM and our
  own python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  ~\cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories, however, the algorithm
  we used sufficiently approximates draws from the marginal distribution and reasonably 
  approximates the correlation structure. We added an empirical correction to enhance
  the accuracy of the correlation structure (see Section~\ref{S-section:flm_correlation}
  of the Supporting Information).

@@

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. Therefore, there is no need to subject
  our trajectories to any reduction in dimensionality. 
  %However, we do adopt the
  %validation techniques used in the packages mentioned above. 
  The states we've 
  chosen include all combinations of trapping mechanisms in the pore and out of
  the pore (see Table~\ref{table:states}). We use the same radial cut-off (0.75 nm)
  as in the anomalous diffusion model to differentiate the pore and tail region. 
  These state choices assume that there are no significant kinetic effects resulting
  from solute conformational changes or pore size fluctuations, an assumption that
  may be relaxed in future work.

@@

  We verified the Markovianity of our process by analyzing the transition matrix. An 
  important condition of a Markov process is the satisfaction of detailed balance:
  \begin{equation}
  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
  \end{equation}
  where $P$ is the equilibrium distribution of states. In other words, the number of
  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
  test is to verify that $T$ holds up to a coarser time scale.~\cite{swope_describing_2004}
  We verified these properties in Section~\ref{S-section:markov_validation} of the 
  Supporting Information.

@@

  The trapping mechanisms affect each solute to varying degrees. The probabilities
  of occupying a given state at any time are plotted in Figure~\ref{fig:state_probabilities}.
  Urea and ethylene glycol spend 56 \% and 44 \% of their time in the tails
  respectively. Urea's compact and flat structure allows it to more easily 
  partition into the tails while ethylene glycol prefers the pore region due to 
  its two hydrophilic hydroxyl groups.

>>>>

%MRS4: Overall - providing a bit gentler easing into the modeling would help. A more clearly articulated overall picture of what the goals of the modeling are.  Does it have to be perfect? Is the main goal just predictive time series, or mechanistic understanding?  Help people a bit more to understand what success or failure would look like.  Help make it clear why the specific models are chosen to investigate. 
%MRS4: To what extent can findings be related back to molecular details?
%MRS4: what are the consequences of the findings?

\title{Time Series Modeling of Subdiffusive Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
%MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
%MRS4: can we turn this into a thesis statement (we find X) rather than a topic statement (we studied X).  Something about the complexity of the models required to get the subdiffusive behavior right?
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories, in order
  to predict solute mean squared displacements (MSDs). With our first model, based
  on the anomalous diffusion literature, we show how solute dynamics can be modeled as
  a fractional diffusion process subordinate to a continuous time random walk.
  We parameterize the distribution of dwell times, hop lengths between dwells and
  correlation between hops. We explore 2 variations of the model. The first variation
  applies a single set of parameters to the solutes and the second applies 2 sets
  of parameters based on the solute's radial distance from the closest pore center.
  Our second model, an adaptation of Markov state models, treats the 
  %MRS4: I don't think this quite captures what is going on, tried to rephrase.
  %system as a Markov process, where we quantify the transitions between a set of 
  %explicitly defined states. 
  configurational state of the system as a Markov process, each of which has state dependent transport behavior.
  We 
  %MRS4: tweaked
  %incorporate 
  fit
  the magnitude and temporal correlation
  of positional fluctuations into each state and transitions between states to gain
  further insight and allow us to predict solute MSDs. We show that our models 
  reasonably reproduce MSDs calculated from molecular simulations. The anomalous 
  diffusion shows superior predictive performance, in many cases 
  %exactly 
  reproducing
  MD results
  %MRS4: added
  well 
  within error. 
  %MRS4: next two sentences seem somewhat repetitive
  We use the parameters of each model to offer additional mechanistic
  insight. These parameters are important for identifying specific differences in 
  solute transport behavior. The differences suggest modifications that can be
  made to LLC membrane monomers in order to increase or reduce selectivity towards a 
  specific solute
  %MRS4: added
  or class of solutes.
  \end{abstract}

@@

  Mathematical descriptions of transport in complex separations membranes are a powerful 
  way to understand mechanisms and formulate membrane design principles. 
  %MRS4: are there citations for the above, like reviews?
  The complexity
  of a model generally parallels the complexity of the transport mechanism at hand, 
  well as 
  the transport information the model conveys.
  %the desired outputs. 
  In dense homogeneous membranes, the solution-diffusion 
  model can extract diffusion and partition coefficients and has successfully predicted
  solute transport rates. 
  %MRS4: citation above?
  Analogously, pore-flow models yield predictions of diffusion 
  coefficients and solute transport rates in nanoporous membranes.~\cite{wijmans_solution-diffusion_1995}
  Modern single particle tracking approaches take us beyond continuum modeling and 
  allow us to characterize complex diffusive behavior.~\cite{manzo_review_2015} 
  At the molecular level, one can use molecular dynamics (MD) simulations to study both
  single particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
  All of these approaches facilitate speculation on the molecular origins of separations
  by attempting to give a more intuitive understanding of how solutes move as a function
  of their environment, in turn suggesting experiments that 
  %should be run.
  could be performed
  % BJC1: tie this paragraph into above by commenting that highly selective membranes
  % often have complex mechanistic reasons that aren't explained by simpler models
  % BJC3:maybe change this paragraph to just be examples of highly selective separations, not
  %MRS4: below - seems to just be about need for selective membranes, not the design of them.
  Facile design
  of highly selective separations membranes is desirable in numerous
  applications. The ability to efficiently separate ions from saline water sources using 
  membranes has been actively pursued for years in an effort to create potable water for 
  people in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  there is a strong interest in creating breathable barriers to chemical warfare agents
  which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
  The speed at which we achieve these or any other selective separation will be 
  heavily influenced by the quality of insights gained by the modeling approaches above.

@@

%  Regardless of which LLC phase ones studies, one must contend with the large chemical design
%  space available to design these types of membranes. 
  We 
  %MRS4: proposed change
  %want to use a molecular model in order to understand how we can leverage the large 
  %chemical space available for LLC monomer design in order to create efficient solute-specific
  %separations. 
  Molecular modeling may make it possible to create efficient solute-specific
  separation membranes using the available chemical space of LLC monomers.
  To date, only a limited subset of LLC monomers have been studied in membrane
  applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, 
  %there have been shown
  they have demonstrated selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling 
  %MRS4
  %provides 
  can provide
  the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms, allowing us to move beyond 
  %traditional 
  %MRS4: above: some would argue lots of design approaches are traditional, not just Edisonian
  Edisonian design approach.

@@

  %MRS4: consider more citations below, when you talk about what researchers have done.
  Researchers have developed a rigorous theoretical foundation for describing the 
  motion of particles exhibiting non-Brownian, or anomalous, transport behavior.
  The tools introduced by fractional calculus are instrumental to this theory. They
  allow us to generalize the normally linear diffusion equation to fractional
  derivative orders, providing descriptions of a much more diverse set of behavior.~\cite{klages_anomalous_2008}

@@

  % BJC2: moved this from below
  Our first modeling approach is based on the anomalous diffusion literature, 
  applying the mathematical formalism describing subdiffusive transport to observed
  solute trajectories. We fit anomalous diffusion models in two ways: 
  %MRS4: can you clarify the sentence below?  Probably something like: uses a single set of parameters in the diffusion equations, etc.
  First, based on a single set of parameters. Second, we use a two-state approach incorporating
  two sets of parameters based on a solute's radial distance from the closest pore center.

  While elegant, pure anomalous diffusion theory may in some cases give only a 
  qualitative understanding of transport mechanisms. 
  %MRS4: might need to provide a bit more explanation why it would be ony qualitative.  
  %Relating it to molecular scale behavior and examples might help.
  Complex temporal relationships in 
  between hops may have a significant effect on the average MSD. Inhomogeneity of 
  a medium or multiple types of interactions may lead to a number of distinct 
  diffusive regimes. In this case, a state based model may be useful.

@@

  Our second modeling approach applies an extended MSM framework to a relatively 
  small set of known states based on the three observed solute trapping mechanisms.
  %MRS4: but yours assume first order state kinetics as well.
  Standard MSMs assume first order kinetics and are typically applied 
  towards determining equilibrium populations of and the transitions between 
  various state configurations.~\cite{bowman_using_2009} 
  %MRS4: this probably needs to be explained more explicitly, that the coordinates of the solute are generated according to the current state. 
  We extend the framework
  to include dynamics within states and between jumps. 
  %MRS4: It makes sense to me what the below is, but probably isn't clear enough for others. 
  That is we parameterize 
  and incorporate into our model the magnitude and temporal correlation of
  fluctuations in solute position while in each state as well as during transitions
  to different states. 
  %Temporal correlation in position has a significant influence on 
  %a solute's mean squared displacement.

@@

  We studied transport of solutes in the H\textsubscript{II} phase using an atomistic
  molecular model of four pores in a monoclinic unit cell with 10\% water by weight 
  (see Figure~\ref{fig:membrane_structure}). Approximately one third of the water 
  molecules occupy the tail region with the rest near the pore center. We chose to
  focus our study on the 10 wt\% water system because solutes move significantly 
  faster than in the 5 wt\% system studied previously. Appropriate stochastic 
  modeling requires that solutes sample the accessible mechanisms with representative
  probability.

@@

  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
  to collect ample data. We simulated the system with a time step of 2 fs at a pressure
  of 1 bar and 300 K controlled by the Parrinello-Rahman barostat and the v-rescale 
  thermostat respectively. We recorded frames every 0.5 ns.

  We considered each system to be equilibrated when the solute partitioning between the 
  pore and tail region %stopped changing. 
  reaches apparent equilibrium.
  %MRS4: added
  and use only data after that point in our analysis of solute kinetics.
  %We excluded data collected before equilibration
  %from our analysis. 
  We plot the solute partition versus time in Figure~\ref{S-fig:equilibration}
  of the Supporting Information in order to justify our choice of equilibration times
  for each solute.

@@

  % BJC3: x --> z since I'm measuring diffusion in the z direction?
  %MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x.  
  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, rather it follows a power law of the form:
  \begin{equation} 
  \langle x^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. A value of $\alpha_d < 1$ indicates a subdiffusive process, 
  while values of $\alpha_d = 1$ and $\alpha_d > 0$ are characteristic of Brownian and
  superdiffusive motion respectively.

@@

  %BJC3: removed ensemble MSD because it's not used
  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. 
  %MRS4: probably need to explain in what way it is non-ergodic below, and if this is the scenario that people should care about.
  If the underlying 
  subdiffusive process is not ergodic, like a pure CTRW, the time averaged MSD becomes
  linear.~\cite{meroz_toolbox_2015}

@@

  %MRS4: Tweak
  %We believe that 
  The solute motion in the system studied here may be consistent with 
  subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
  the leading process is a CTRW. We observe hopping and trapping which is consistent
  with a CTRW, along with negatively correlated hops which is consistent with FBM.

  One can characterize a CTRW process 
  %using 
  by 
  the parameters which describe its dwell 
  time and hop length distributions. We used the \texttt{ruptures} python package in 
  order to automatically identify mean shifts in solute trajectories, indicating hops.\cite{truong_ruptures:_2018} 
  We used the corresponding hop lengths and dwell times between hops to construct 
  empirical distributions.

@@

  Assuming hops are correlated, solute behavior may be described by subordinated 
  fractional L\'evy motion (sFLM). The Hurst parameter can again be used to describe
  hop correlations because they share the same autocorrelation structure.~\cite{tikanmaki_fractional_2010}
  The autocovariance function for FLM is:
  \begin{equation}
    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)\sin(\pi H)}
    \label{eqn:flm_autocovariance}
  \end{equation}
  where $E\big[L(1)^2\big]$ is the expected value of squared draws from the 
  underlying L\'evy distribution, effectively the distribution's 
  variance.~\cite{bishwal_maximum_2011} In general, most L\'evy stable distributions
  have an undefined variance due to their heavy tails. However, normalizing
  Equation~\ref{eqn:flm_autocovariance} by the variance of a finite number of draws
  from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
  See Section~\ref{S-section:H_estimate} of the Supporting Information for numerical
  simulations illustrating this point.  % BJC3: could use another reference proving mathematically what I show numerically

@@

  %MRS4: should be more clear which of the two kinetics scenarios this next assumption applies to
  \subsubsection*{Multiple Dynamical Modes}

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This inspired two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
%  $\alpha$, $\sigma$, $H$ and, when the truncated power law is used, $\lambda$ parameters
%  fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  %MRS4: some justification on why 0.75 vs. any other cutoff.
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  %MRS4: Do you assume Markovian behavior in transitions between the states?  Be explicit.
  \subsubsection*{Simulating Anomalous Diffusion}

  %MRS4: tweaked: otherwise sounds like you simulated all parameters values as well.
  We simulated models with all combinations of 
  the types of 
  dwell and hop length distributions
  described above, which are summarized in Table~\ref{table:anomalous_models}. All models 
  include correlation between hops.
  %MRS4: not abbreviations are not necessarily defined: should be defined above, perhaps? (i.e. we will refer X as 'sFBMcut')
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{|c|c|c|}
	  \hline
	  Dwell Distribution                & Hop Length Distribution & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
	  \end{tabular}
	  \caption{We tested models with various modifications to the dwell and hop
	  length distributions. We incorporate correlation structure into all models.}\label{table:anomalous_models}
 \end{table}

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 10000 anomalous diffusion trajectories of length $T_{sim}$ in
  order to directly compare our model's predictions to MD simulations. $T_{sim}$ varied due to
  differing solute equilibration times. We constructed trajectories by simulating 
  sequences of dwell times and correlated hop lengths generated based on
  parameters randomly chosen from our bootstrapped parameter distributions. We 
  propagated each trajectory until the total time equaled or exceeded $T_{sim}~ \mu$s, then
  truncated the last data point so that the total time exactly equaled $T_{sim}~ \mu$s since
  valid comparisons are only possible between fixed length sFBM simulations. The
  power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
  decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
  We reported the time-averaged MSD after time lags 40\% the length of the trajectory
  with corresponding 95\% intervals.
  %BJC3: Not sure if 40 % above is too long. I could do 20
  %MRS4: is there some rule of thumb that could be used to justify the choice?
  When simulating 2 mode models, we determined the state sequence based on random 
  draws weighted by the appropriate row of the probability transition matrix. We 
  %MRS4: not quite sure what you mean by incorporating uncertainty. 
  incorporated uncertainty into transition probabilities by drawing samples from a 
  two dimensional Dirichlet distribution (also called a beta distribution) with concentration parameters defined by 
  the count matrix.~\cite{bacallado_bayesian_2009} We drew hops and dwells based on
  the current state of the system. 
  %MRS4: you saiid this a couple of paragraphs before. 
  We used a single Hurst parameter to describe
  correlation between hops, independent of the solute's mode. Ideally, each mode
  would have its own Hurst parameter, but we did not observe enough long sequences
  of uninterrupted time spent in each mode with which to generate robust
  autocorrelation functions.

  %We also projected MSDs out to 1 second for each solute. % BJC3:??
  %BJC3: not sure how to cite fbm
  We used the python package \texttt{fbm} to generate exact simulations of FBM and our
  own python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  ~\cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories, however, the algorithm
  we used sufficiently approximates draws from the marginal distribution and 
  reasonably 
  approximates the correlation structure. We added an empirical correction to enhance
  the accuracy of the correlation structure (see Section~\ref{S-section:flm_correlation}
  of the Supporting Information
  %MRS4: added 
  for validation of the approach 
  ).

@@

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. Therefore, there is no need to subject
  %MRS4: not clear what dimensionality is being referred to here.
  our trajectories to any reduction in dimensionality. 
  %However, we do adopt the
  %validation techniques used in the packages mentioned above. 
  The states we've 
  chosen include all combinations of trapping mechanisms in the pore and out of
  the pore (see Table~\ref{table:states}). We use the same radial cut-off (0.75 nm)
  as in the anomalous diffusion model to differentiate the pore and tail region. 
  These state choices assume that there are no significant kinetic effects resulting
  from solute conformational changes or pore size fluctuations, an assumption that
  may be relaxed in future work.

@@

  %MRS4: here, be more explicit you are testing the validity of the Markovian approximation on the molecular data.
  We verified the Markovianity of our process by analyzing the transition matrix. An 
  important condition of a Markov process is the satisfaction of detailed balance:
  \begin{equation}
  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
  \end{equation}
  where $P$ is the equilibrium distribution of states. In other words, the number of
  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
  test is to verify that $T$ holds up to a coarser time scale.~\cite{swope_describing_2004}
  We verified these properties in Section~\ref{S-section:markov_validation} of the 
  Supporting Information.

@@

  The trapping mechanisms affect each solute to varying degrees. The probabilities
  of occupying a given state at any time are plotted in Figure~\ref{fig:state_probabilities}.
  Urea and ethylene glycol spend 56\% and 44\% of their time in the tails
  respectively. Urea's compact and flat structure allows it to more easily 
  partition into the tails while ethylene glycol prefers the pore region due to 
  its two hydrophilic hydroxyl groups.
